Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 \MakeLowercase{b}

### 2018-10-09 ms.tex
removed the H-alpha stuff because now we realize the spike was an artifact of the data cleaning.

The high resolution spectrum of \shStar\ \citep{kawahara2013starspots} showed a different temperature and gravity than photometric methods \cite[e.g.][]{brown2011kic,huber2014kicprop}.
\citet{vanlieshout2016kic1255} suggest that one exciting possibility is that gases from the disintegrating planet contaminate the high resolution spectrum.
This would enable compositional and kinematic studies of the disintegrating planet.
In Section \ref{sec:stellarCharacterization}, we examine archival Subaru High Dispersion Spectrograph (HDS) spectra of the star to assess the stellar parameters and explore the possibility that sublimated gases appear in the high resolution spectrum.
\added{In Section \ref{sec:activity}, we examine the activity of the star from the H$\alpha$ line and also discuss how starspots can affect the light curves.}
We conclude in Section \ref{sec:conclusions}.

@@

The high resolution spectrum of \shStar\ allows us to measure the H$\alpha$ line, which is an indicator of stellar activity.
Figure \ref{fig:Halpha}, shows the Subaru HDS spectrum for 2015 Aug 28 and 2015 Aug 29.

We note that the strong emission feature at the core of the H$\alpha$ line is visible for one night but not the other, confirming the activity of the star already known from the rotational modulations \citep{kawahara2013starspots}.

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.8\textwidth]{h_alpha_subaru.pdf}
\caption{H$\alpha$ line as measured by Subaru HDS on two adjacent nights in 2015.
The line's core changes noticeably between the two nights.}\label{fig:Halpha}
\end{centering}
\end{figure*}

>>>>

The high resolution spectrum of \shStar\ \citep{kawahara2013starspots} showed a different temperature and gravity than photometric methods \cite[e.g.][]{brown2011kic,huber2014kicprop}.
\citet{vanlieshout2016kic1255} suggest that one exciting possibility is that gases from the disintegrating planet contaminate the high resolution spectrum.
This would enable compositional and kinematic studies of the disintegrating planet.
In Section \ref{sec:stellarCharacterization}, we examine archival Subaru High Dispersion Spectrograph (HDS) spectra of the star to assess the stellar parameters and explore the possibility that sublimated gases appear in the high resolution spectrum.
\added{In Section \ref{sec:activity}, we examine how un-occulted starspots can affect the transit depth behavior.}
We conclude in Section \ref{sec:conclusions}.

@@
